RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-09-23 manuscripts/manuscript.Rmd
omit rrdf

---
#layout: preprint
layout: review, 11pt
linenumbers: true
title: "RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Scott Chamberlain
    affiliation: ropensci
  - name: Rutger Vos
    affiliation: NBC
  - name: Hilmar Lapp
    affiliation: dukeplus
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: ropensci
    address: |
      University of California, Berkeley, CA, USA
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
  - code: dukeplus
    address: | 
      Center for Genomic and Computational Biology, Duke University,
      and 
      National Evolutionary Synthesis Center, Durham, NC, USA
abstract: | 
      1. NeXML is a powerful and extensible exchange standard
      recently proposed to better meet the expanding needs for
      phylogenetic data and metadata sharing. Here we
      present the RNeXML package, which provides users of
      the R programming language with easy-to-use tools for 
      reading and writing NeXML documents, including rich metadata, in
      a way that interfaces seamlessly with the extensive library of
      phylogenetic tools already available in the R ecosystem.

>>>>

---
#layout: preprint
layout: review, 11pt
linenumbers: true
title: "RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R"
author: 
  - name: Carl Boettiger
    affiliation: ucb
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Scott Chamberlain
    affiliation: ropensci
  - name: Rutger Vos
    affiliation: NBC
  - name: Hilmar Lapp
    affiliation: dukeplus
address: 
  - code: ucb 
    address: |
      University of California, Berkeley,
      130 Mulford Hall \#3114,
      Berkeley, CA 94720-3114, USA 
  - code: ropensci
    address: |
      University of California, Berkeley, CA, USA
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
  - code: dukeplus
    address: | 
      Center for Genomic and Computational Biology, Duke University,
      and 
      National Evolutionary Synthesis Center, Durham, NC, USA
abstract: | 
      1. NeXML is a powerful and extensible exchange standard
      recently proposed to better meet the expanding needs for
      phylogenetic data and metadata sharing. Here we
      present the RNeXML package, which provides users of
      the R programming language with easy-to-use tools for 
      reading and writing NeXML documents, including rich metadata, in
      a way that interfaces seamlessly with the extensive library of
      phylogenetic tools already available in the R ecosystem.
